---
title: "Project"
output: html_document
date: "2024-11-16"
---

## Read Data

```{r}
library(readr)

# Define the path to the CSV file in the "arxiv" folder
file_path <- file.path("archive", "df_train.csv")  # Replace 'your_file.csv' with the actual file name

# Read the CSV file
data_train <- read_csv(file_path)

file_path2 <- file.path("archive", "df_test.csv")  # Replace 'your_file.csv' with the actual file name

# Read the CSV file
data_test <- read_csv(file_path2)

# Display the first few rows of the data
print(data_train)
```

## Preprocessing

```{r}


library(dplyr)

# Convert specific columns to factors with labels "0" and "1"
dataset_train <- data_train %>%
  mutate(across(
    c(has_basement, renovated, nice_view, perfect_condition, has_lavatory, single_floor),
    ~ factor(., labels = c(0, 1))
  ))

dataset_test <- data_test %>%
  mutate(across(
    c(has_basement, renovated, nice_view, perfect_condition, has_lavatory, single_floor),
    ~ factor(., labels = c(0, 1))
  ))
if (!requireNamespace("lubridate", quietly = TRUE)) {
  install.packages("lubridate")
}
library(lubridate)



dataset_test <- dataset_test %>%
  mutate(date = as.numeric(date))  # Converts 'date' column to numeric (days since 1970-01-01)

dataset_train <- dataset_train %>%
  mutate(date = as.numeric(date)) 

```

```{r}

library(dplyr)

# Replace non-numeric columns in-place
dataset_train <- dataset_train %>%
  mutate(across(everything(), ~ as.numeric(as.character(.))))

# Check for remaining non-numeric columns
non_numeric_cols <- sapply(dataset_train, function(col) !is.numeric(col))
if (any(non_numeric_cols)) {
  print("Non-numeric columns remain:")
  print(names(dataset_train)[non_numeric_cols])
} else {
  print("All columns are now numeric.")
}

print(dataset_train)
```

```{r}
# Install and load ggcorrplot
if (!requireNamespace("ggcorrplot", quietly = TRUE)) {
  install.packages("ggcorrplot")
}
library(ggcorrplot)

# Assuming your dataset is named `dataset_train`
# Calculate the correlation matrix (only numeric columns)
cor_matrix <- cor(dataset_train)

# Plot the correlation matrix with adjusted sizes
ggcorrplot(
  cor_matrix,
  lab = TRUE,               # Show correlation coefficients
  lab_size = 3,             # Smaller label size for numbers in the cells
  tl.cex = 5,              # Smaller text label size for axis labels
  colors = c("red", "white", "blue"), # Custom color palette
  title = "Correlation Matrix"
)


```

```{r}
ggplot(dataset_train, aes(x = grade, y = living_in_m2, fill = as.factor(grade))) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +  # Change to bar chart
  scale_fill_viridis_d(option = "C") +                           # Use a Viridis color palette
  labs(
    title = "Living Space by grade",
    x = "grade",
    y = "living_space",
    fill = "grade"
  ) +
  theme_minimal() +                                              # Change the theme for a cleaner look
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),           # Center and enlarge the title
    axis.text = element_text(size = 12),                        # Enlarge axis text
    axis.title = element_text(size = 14),                       # Enlarge axis titles
    legend.position = "right"                                   # Move legend to the right
  )

```

```{r}
library(ggplot2)
#install.packages("viridis")

library(viridis)

ggplot(dataset_train, aes(x = bedrooms, y = living_in_m2, fill = as.factor(bedrooms))) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +  # Change to bar chart
  scale_fill_viridis_d(option = "C") +                           # Use a Viridis color palette
  labs(
    title = "Living Space by Number of Bedrooms",
    x = "Number of Bedrooms",
    y = "Living Space (m²)",
    fill = "Bedrooms"
  ) +
  theme_minimal() +                                              # Change the theme for a cleaner look
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),           # Center and enlarge the title
    axis.text = element_text(size = 12),                        # Enlarge axis text
    axis.title = element_text(size = 14),                       # Enlarge axis titles
    legend.position = "right"                                   # Move legend to the right
  )

```

```{r}

ggplot(dataset_train, aes(x = grade, y = bedrooms, fill = as.factor(grade))) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +  # Change to bar chart
  scale_fill_viridis_d(option = "C") +                           # Use a Viridis color palette
  labs(
    title = "bedrooms by grade",
    x = "grade",
    y = "bedrooms",
    fill = "grade"
  ) +
  theme_minimal() +                                              # Change the theme for a cleaner look
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),           # Center and enlarge the title
    axis.text = element_text(size = 12),                        # Enlarge axis text
    axis.title = element_text(size = 14),                       # Enlarge axis titles
    legend.position = "right"                                   # Move legend to the right
  )
```

```{r}

ggplot(dataset_train, aes(x = grade, y = price, fill = as.factor(grade))) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +  # Change to bar chart
  scale_fill_viridis_d(option = "C") +                           # Use a Viridis color palette
  labs(
    title = "price by grade",
    x = "grade",
    y = "price",
    fill = "grade"
  ) +
  theme_minimal() +                                              # Change the theme for a cleaner look
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),           # Center and enlarge the title
    axis.text = element_text(size = 12),                        # Enlarge axis text
    axis.title = element_text(size = 14),                       # Enlarge axis titles
    legend.position = "right"                                   # Move legend to the right
  )
```

```{r}

ggplot(dataset_train, aes(x = bedrooms, y = price, fill = as.factor(bedrooms))) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +  # Change to bar chart
  scale_fill_viridis_d(option = "C") +                           # Use a Viridis color palette
  labs(
    title = "price by bedrooms",
    x = "bedroooms",
    y = "price",
    fill = "grade"
  ) +
  theme_minimal() +                                              # Change the theme for a cleaner look
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),           # Center and enlarge the title
    axis.text = element_text(size = 12),                        # Enlarge axis text
    axis.title = element_text(size = 14),                       # Enlarge axis titles
    legend.position = "right"                                   # Move legend to the right
  )

```

```{r}

ggplot(dataset_train, aes(x = real_bathrooms, y = price, fill = as.factor(real_bathrooms))) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +  # Change to bar chart
  scale_fill_viridis_d(option = "C") +                           # Use a Viridis color palette
  labs(
    title = "price by bathrooms",
    x = "bathroom",
    y = "price",
    fill = "grade"
  ) +
  theme_minimal() +                                              # Change the theme for a cleaner look
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),           # Center and enlarge the title
    axis.text = element_text(size = 12),                        # Enlarge axis text
    axis.title = element_text(size = 14),                       # Enlarge axis titles
    legend.position = "right"                                   # Move legend to the right
  )
```

```{r}

ggplot(dataset_train, aes(x = nice_view, y = price, fill = as.factor(nice_view))) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +  # Change to bar chart
  scale_fill_viridis_d(option = "C") +                           # Use a Viridis color palette
  labs(
    title = "price by nice view",
    x = "nice view",
    y = "price",
    fill = "nice view"
  ) +
  theme_minimal() +                                              # Change the theme for a cleaner look
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),           # Center and enlarge the title
    axis.text = element_text(size = 12),                        # Enlarge axis text
    axis.title = element_text(size = 14),                       # Enlarge axis titles
    legend.position = "right"                                   # Move legend to the right
  )
```

```{r}

ggplot(dataset_train, aes(x = quartile_zone, y = price, fill = as.factor(quartile_zone))) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +  # Change to bar chart
  scale_fill_viridis_d(option = "C") +                           # Use a Viridis color palette
  labs(
    title = "price by zone",
    x = "zone",
    y = "price",
    fill = "zone"
  ) +
  theme_minimal() +                                              # Change the theme for a cleaner look
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),           # Center and enlarge the title
    axis.text = element_text(size = 12),                        # Enlarge axis text
    axis.title = element_text(size = 14),                       # Enlarge axis titles
    legend.position = "right"                                   # Move legend to the right
  )
```

## MLR Model
```{r}
# Fit the Multiple Linear Regression model
mlr_model <- lm(price ~ bedrooms + grade + has_basement + living_in_m2 + renovated + nice_view +
                  perfect_condition + real_bathrooms + has_lavatory + single_floor +
                  month + quartile_zone, data = dataset_train)

# Display the model summary
summary(mlr_model)

```
### Model Summary


### Interpretations:
- **Significant Predictors**: All predictors have p-values < 0.05, indicating statistical significance.
- **Strongest Predictors**:
  - `living_in_m2`: A critical driver of house prices.
  - `grade`: Higher grades significantly increase house prices.
  - `quartile_zone`: Highlights the importance of location.


- **Residual Standard Error**: \( 0.01665 \), indicating a good fit.
- **Multiple R-squared**: \( 0.7628 \), meaning approximately 76% of the variance in log(price) is explained by the model.
- **Adjusted R-squared**: \( 0.7625 \), accounting for the number of predictors.
- **F-statistic**: \( 3121 \), p-value < \( 2.2e^{-16} \), confirming overall model significance.
```{r}

# Residuals vs Fitted Plot
plot(mlr_model, which = 1, main = "Residuals vs Fitted")

# Normal Q-Q Plot
plot(mlr_model, which = 2, main = "Normal Q-Q")

# Histogram of Residuals
hist(residuals(mlr_model), breaks = 30, main = "Histogram of Residuals", xlab = "Residuals")

```
There is a slight curve in the Residuals vs Fitted Plot suggeesting that the model is missing some non-linear relationships.

Deviations at the Ends in the QQ plot suggests suggest skewness or heavy tails in the residuals.

## Instrumental Variables (IV) 

### First Stage
```{r}
# Ensure renovated is numeric
dataset_train$renovated <- as.numeric(as.character(dataset_train$renovated))

# First Stage Regression
first_stage_model <- lm(renovated ~ grade + quartile_zone, data = dataset_train)

# Display summary of the first stage regression
summary(first_stage_model)
```
#### Interpretation
- The **Intercept** is significant, indicating that when all predictors are zero, the baseline value of `renovated` is approximately 0.0473.
- The variable `grade` has a negative and significant effect on `renovated`, with a small but statistically significant estimate (-0.0082, p < 0.001).
- The instrument `quartile_zone` shows mixed results:
  - **quartile_zone3** and **quartile_zone4** have significant positive coefficients (p < 0.001), indicating that properties in these zones are more likely to be renovated.
  - **quartile_zone2**, however, is not significant (p = 0.288).

- **Residual Standard Error (RSE)**: 0.193  
  The residuals indicate that the model captures only a small amount of variation in `renovated`.
  
- **Multiple R-squared**: 0.003466  
  This value indicates that only ~0.35% of the variation in `renovated` is explained by `grade` and `quartile_zone`. While low, this is not uncommon in first-stage regressions for binary variables.

- **Adjusted R-squared**: 0.003172  
  Adjusted for the number of predictors, the R-squared value remains very low.

- **F-statistic**: 11.82 (p < 0.001)  
  The F-statistic confirms that the model is statistically significant overall, suggesting that the predictors, collectively, have some explanatory power.

The first-stage regression results demonstrate partial **relevance** for the instrument `quartile_zone`. While `quartile_zone3` and `quartile_zone4` are significant predictors of `renovated`, `quartile_zone2` is not. The F-statistic exceeds the threshold of 10, supporting the instrument's overall strength in explaining `renovated`.
### Second Stage
```{r}
# Add predicted values of renovated from the first stage
dataset_train$hat_R <- predict(first_stage_model)

# Second Stage Regression
second_stage_model <- lm(price ~ bedrooms + grade + hat_R + nice_view +
                           living_in_m2 + perfect_condition + quartile_zone, 
                         data = dataset_train)

# Display summary of the second stage regression
summary(second_stage_model)
```
####  Interpretation
- **Residual Standard Error (RSE)**: 0.01687  
  This indicates a close fit of the model to the data, with small residuals overall.
  
- **Multiple R-squared**: 0.7565  
  Approximately 75.65% of the variation in house prices is explained by the predictors in the model.
  
- **Adjusted R-squared**: 0.7564  
  This value accounts for the number of predictors in the model, confirming a strong fit even when adjusted for complexity.
  
- **F-statistic**: 5279 (p < 2.2e-16)  
  The F-statistic is highly significant, suggesting that the model explains a substantial portion of the variation in house prices.

The second-stage regression demonstrates that the instrumented variable `hat_R` (renovation status) has a strong positive effect on house prices, supporting the hypothesis that renovations increase property value. All other variables are statistically significant, and the model explains a large portion of the variance in house prices. The results suggest that the instrumented renovations are indeed a key determinant of house prices, and the IV method provides a reliable estimate of their causal effect.
```{r}
plot(second_stage_model, which = 1, main = "Residuals vs Fitted")
plot(second_stage_model, which = 2, main = "Normal Q-Q")
hist(residuals(second_stage_model), breaks = 30, main = "Histogram of Residuals", xlab = "Residuals")

```
Both the residuals vs. fitted plot and the Q-Q plot suggest that the model might benefit from further refinement. The curvature in the residuals suggests possible non-linear relationships, while the non-normality of the residuals indicates the need for additional steps to improve the model fit and the validity of the estimates.

## Fixed-Effects Model

```{r}
# Fit the Fixed-effects Model
fixed_effects_model <- lm(price ~ bedrooms + living_in_m2 + nice_view + perfect_condition + quartile_zone, data = dataset_train)

# Display summary of the fixed-effects model
summary(fixed_effects_model)
```
### Interpretation
The fixed-effects model was estimated to account for unobserved location-specific factors that may influence house prices. The results are as follows:

- **Intercept**: The baseline house price is estimated at \$2.487, which is highly significant.
- **Bedrooms**: The number of bedrooms has a negligible and statistically insignificant effect on house prices (p-value = 0.988).
- **Living Area**: Each additional square meter of living area increases the house price by 0.0245%, and this effect is highly significant (p-value < 2e-16).
- **Nice View**: Having a nice view increases house prices by 1.57%, which is highly significant (p-value < 2e-16).
- **Perfect Condition**: Properties in perfect condition increase in price by approximately 0.68%, with a highly significant p-value (p-value < 2e-16).
- **Quartile Zones**: The coefficients for quartile zones indicate significant location-based effects:
  - Quartile Zone 2: +2.39% higher price.
  - Quartile Zone 3: +4.71% higher price.
  - Quartile Zone 4: +5.49% higher price.
  
Overall, the fixed-effects model provides strong evidence that property features such as living area, view, and condition, along with the neighborhood zone, are significant determinants of house prices.

The model has a residual standard error of 0.01751 and explains approximately 73.75% of the variance in house prices (R-squared = 0.7375). The F-statistic is 5458, confirming that the model is statistically significant.


## Sensivity Analysis for each Model

```{r}
# 1. Add interaction term (e.g., living area and number of bedrooms)
mlr_interaction_model <- lm(price ~ bedrooms * living_in_m2 + nice_view + perfect_condition + quartile_zone, data = dataset_train)
summary(mlr_interaction_model)

# 2. Log transformation of the dependent variable (price)
mlr_log_model <- lm(log(price) ~ bedrooms + living_in_m2 + nice_view + perfect_condition + quartile_zone, data = dataset_train)
summary(mlr_log_model)

# 3. Exclude control variable (e.g., remove `nice_view` variable)
mlr_reduced_model <- lm(price ~ bedrooms + living_in_m2 + perfect_condition + quartile_zone, data = dataset_train)
summary(mlr_reduced_model)
```




